\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-13 paper.qmd
Corrected the issue with tSNE AIC calculation

tSNE_data_gau <- read_rds("data/five_gau_clusters/tsne_data_five_gau.rds")
UMAP_data_gau <- read_rds("data/five_gau_clusters/umap_data_five_gau.rds")
PHATE_data_gau <- read_rds("data/five_gau_clusters/phate_data_five_gau.rds")
TriMAP_data_gau <- read_rds("data/five_gau_clusters/trimap_data_five_gau.rds")
PaCMAP_data_gau <- read_rds("data/five_gau_clusters/pacmap_data_five_gau.rds")

>>>>

tSNE_data_gau <- read_rds("data/five_gau_clusters/tsne_data_five_gau_61.rds")
UMAP_data_gau <- read_rds("data/five_gau_clusters/umap_data_five_gau.rds")
PHATE_data_gau <- read_rds("data/five_gau_clusters/phate_data_five_gau.rds")
TriMAP_data_gau <- read_rds("data/five_gau_clusters/trimap_data_five_gau.rds")
PaCMAP_data_gau <- read_rds("data/five_gau_clusters/pacmap_data_five_gau.rds")

### 2024-01-13 paper.tex
Corrected the issue with tSNE AIC calculation

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, sharp corners]}{\end{tcolorbox}}\fi
